Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-08-08 src/tex/ms.tex
Change for B.6
minor text change

Figure \ref{fig:violin_kappa} makes it clear that not all \acp{BBH} in GWTC-3 are equally informative about birefringence.
When considered individually, the events that best constrain $\kappa$ are listed in Table~\ref{tab:best_events_kappa}, in order of increasing standard deviation $\sigma_i$.
That table also shows the credible level (CL) at which the posterior supports $\kappa = 0$, whereby $\mathrm{CL} = 0$ ($\mathrm{CL} = 1$) means the posterior supports that value with high (low) probability.

@@

The result of \citet{Okounkova_2022} is also phrased in terms of a canonical Chern-Simons length scale,\footnote{This results from setting the so-called ``canonical'' Chern-Simons embedding into a FRW cosmology, where the Chern-Simons field evolves as $\theta \propto t$ \cite{Alexander:2009tp,Jackiw:2003pm,Yunes2009}.} 
\begin{equation}
    l_0 = \frac{c d_H \kappa}{3 \pi f} = 1400 \, \mathrm{km} \left( \frac{\kappa}{1 \, \mathrm{Gpc}^{-1}} \right) \left( \frac{100 \, \mathrm{Hz}}{f} \right);
\end{equation}
our 68\% credible bound on $\kappa$ implies $l_0 \lesssim 40 \, \mathrm{km}$ at $100 \, \mathrm{Hz}$.  This compares favorably to the constraint in \citet{Okounkova_2022}, which had $l_0 \lesssim 1000 \, \mathrm{km}$.

>>>>

Figure \ref{fig:violin_kappa} makes it clear that not all \acp{BBH} in GWTC-3 are equally informative about birefringence.
When considered individually, the events that best constrain $\kappa$ are listed in Table~\ref{tab:best_events_kappa}, in order of increasing standard deviation $\sigma_i$.
That table also shows the credible level (CL) at which the posterior supports $\kappa = 0$, whereby $\mathrm{CL} = 0$ ($\mathrm{CL} = 1$) means the posterior supports that value with high (low) probability.
This quantity can be understood as the relative height of the probability density function at a given value, and does not assume any symmetric interval or modality.

@@

The result of \citet{Okounkova_2022} is also phrased in terms of a canonical Chern-Simons length scale\footnote{This results from setting the so-called ``canonical'' Chern-Simons embedding into a FRW cosmology, where the Chern-Simons field evolves as $\theta \propto t$ \cite{Alexander:2009tp,Jackiw:2003pm,Yunes2009}.}, 
\begin{equation}
    l_0 = \frac{c d_H \kappa}{3 \pi f} = 1400 \, \mathrm{km} \left( \frac{\kappa}{1 \, \mathrm{Gpc}^{-1}} \right) \left( \frac{100 \, \mathrm{Hz}}{f} \right);
\end{equation}
our 68\% credible bound on $\kappa$ implies $l_0 \lesssim 40 \, \mathrm{km}$ at $100 \, \mathrm{Hz}$.  This compares favorably to the constraint in \citet{Okounkova_2022}, which had $l_0 \lesssim 1000 \, \mathrm{km}$.
